EGGs are adhesive!

### 2025-03-13 calco/main.tex
Term graphs with closed eq

\begin{definition}
	Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair for $q^\star \circ s$.
	We will say that $\mathcal{G}$ is an \emph{e-hypergraph} if $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.

@@

\begin{definition}\label[definintion]{def:GEqTGs}
	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\egg/R(\mathcal{G}^\Sigma)$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono. The inclusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
\end{definition}

\todo{Here we must introduce $\GEqTGs$}

>>>>

\begin{definition}\label[definition]{def:ehyp1}
	Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair for $q^\star \circ s$.
	We will say that $\mathcal{G}$ is an \emph{e-hypergraph} if $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.

@@

We can now introduce term graphs with closed equivalences.

%\begin{definition}\label[definintion]{def:GEqTGs}
%	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\eggs$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono. The inclusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
%\end{definition}

\begin{definition}\label[definition]{def:GEqTGs}
	Let $\Sigma$ be an algebraic signature. An object $(\mathcal{T}, l)$ of $\eggs$ is an \emph{e-term graph} if $l: T(\mathcal{T})\to \mathcal{G}^\Sigma$ is a term graph. We denote by $\GEqTGs$ the full subcategory of $\eggs$ so defined, and denote by $I_{\GEqTGs}$ the corresponding inclusion functor.
\end{definition}
\noindent
\parbox{8.5cm}{\begin{remark}\label[remark]{rem:inclusions}
	The category $\GEqTGs$ is also a full subcategory of $\EqTGs$, since each object $(\mathcal{H}, l)$ is a term graph with equivalence too.
	We denote the corresponding inclusion functor as $S_\eq$. Hence, we have a situation similiar to the one in \Cref{rem:obv}, as the diagram aside shows, where $T_\eq$ is the inclusion functor of \Cref{def:ehyp1} lifted to the slice category, i.e., is such that $V_\Sigma \circ T_\eq = I \circ V_\eq$.
\end{remark}}
	\hfill\parbox{4.5cm}{\[\xymatrix@R=20pt@C=38pt{\GEqTGs \ar[r]^{I_{\GEqTGs}}  \ar[d]_{S_\eq}& \eggs \ar[d]^{T_\eq} \\ \EqTGs \ar[r]_{I_\eq}& \EqHyp_{\Sigma}}\]}

%\todo{Here we must introduce $\GEqTGs$}
